Recognizing emotions with technology and starting discussions

### 2018-01-21 paper.tex
Add discussion draft

\section{Results}
As described in section \ref{method}, we have conducted prototype testing sessions with 13 participants.
For each of these participants, we have two pieces of data:
\begin{itemize}
    \item{Predicted emotions during the shown video, created by the prototype}
    \item{Results from the interview we had with each participant during the testing}
\end{itemize}
Furthermore, for every of the three available videos, we have expectations regarding the emotions at certain
times of the video. Using these pieces of data, we are interested in the following information from analyzing
the results:
\begin{enumerate}
    \item{Do the participants agree with the emotions predicted by the prototype?}
    \item{Do the predicted emotions coincide with the expectations we had for certain videos?}
\end{enumerate}
The first questions can be answered by cross-checking the data that the prototype generated, against the
answers from the participants during the interview. The second question can be verified by checking the
expected emotions at certain times in a video, against the average of all the participants who watched that
video. This will make it clear whether the expected emotion is also the dominant emotion at that time.
Finally, we can combine questions 1 and 2. If both results are positive; that is, the predicted emotions by the
prototype match up with our expectations, and are valid according to the participant, then we can conclude
that it's highly likely to be accurate.

@@

The analyzing of the data generated by the prototype was done using some custom code. This analyzer tool was
created using Python and the matplotlib\footnote{\url{https://matplotlib.org}}} library to generate the charts.
The analysis tool is available as well: \url{https://github.com/drtheuns/minor_riet_analysis}

@@

@@

\section{Discussion}
To be added

>>>>

\section{Results} \label{results}
As described in section \ref{method}, we have conducted prototype testing sessions with 13 participants.
For each of these participants, we have two pieces of data:
\begin{itemize}
    \item{Predicted emotions during the shown video, created by the prototype}
    \item{Results from the interview we had with each participant during the testing}
\end{itemize}
Furthermore, for every of the three available videos, we have expectations regarding the emotions at certain
times of the video. Using these pieces of data, we are interested in the following information from analyzing
the results:
\begin{enumerate}
    \item{Do the participants agree with the emotions predicted by the prototype?}
    \item{Do the predicted emotions coincide with the expectations we had for certain videos?}
\end{enumerate}
The first questions can be answered by cross-checking the data that the prototype generated, against the
answers from the participants during the interview. The second question can be verified by checking the
expected emotions at certain times in a video, against the average of all the participants who watched that
video. This will make it clear whether the expected emotion is also the dominant emotion at that time.
Finally, we can combine questions 1 and 2. If both results are positive; that is, the predicted emotions by the
prototype match up with our expectations, and are valid according to the participant, then we can conclude
that it's highly likely to be accurate.

@@

The analyzing of the data generated by the prototype was done using some custom code. This analyzer tool was
created using Python and the matplotlib\footnote{\url{https://matplotlib.org}} library to generate the charts.
The analysis tool is available as well: \url{https://github.com/drtheuns/minor_riet_analysis}

@@

Based on the above charts regarding the measured emotions versus the expected emotions, in most cases the
expectations seems to have come true. In figure \ref{chart_neck}, however, the expectation of disgust between
23 and 25 seconds seems to have been wrong, as happiness seems to be the most dominant emotion. Towards the end
of \emph{Neck}, there is also an increase in chance for happiness, alongside disgust.

Another interesting moment can be seen in figure \ref{chart_failarmy} around 12.5 seconds into the video (x=25).
Disgust takes over for a short moment in between two moments where happiness had been the emotion with the
highest percent chance.

@@

\section{Discussion}
In section \ref{results} we defined two questions that, when answered, can give a more conclusive image of the
results. Here we will explore our interpretation of the data and answer these questions.

Our first question was: \emph{Do the participants agree with the emotions predicted by the prototype?}.
Out of the 13 research participants, X agreed that the emotions depicted by the prototype, were correct with
how they felt. Therefore, we can conclude that yes, the participants mostly agreed with the results from the
prototype. One emotion often stood out as possibly wrong, namely \emph{disgust}. Many people also agreed,
however, that this might be because of they way they look normally. This could mean that either people often
look with disgust by default, or that neutral and disgust were not properly distinguished from each other by
the prototype. This could be solved by either letting the participants review the video of themselves to see
if they agree with the judgment of the prototype, or by improving the dataset used to train the SVM model,
thereby increasing the accuracy.

Our second question, \emph{Do the predicted emotions coincide with the expectations we had for certain videos?},
can largely be answered by looking at the charts. Here we can see that in most cases, the expectations and
predicted emotions by the prototype match. Only in 1 instance was the expected emotion wrong from the measured
emotions. This was the expectation of disgust around 23 to 25 seconds in the \emph{Neck} video. One possible
explanation for this discrepancy could be the small amount of people that have watched the video (3 people). 
It is possible that a single participant skewed the results because they attribute for a third of the average.
In all cases, however, the relatively small number of participants could mean that there is not enough data to
give a conclusive answer.

If we combine the positive answers for both of the above questions, we get a fairly clear image of the accuracy
and usability of the prototype. Although further improvements are necessary, for example a larger dataset,
the prototype works sufficiently well to be used in starting a discussion. Out of 13 participants, X agreed that
the visualization, especially in group settings, is capable of helping in starting a discussion regarding their
emotions on a specific subject.
